Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-10-12 paper.tex
typo

If we were to adopt \coqe!state! as our actual representation, the
memory usage of the resulting program would quite poor. It would take
at least 128 bytes to store that many bits (assuming that booleans are
stored in the smallest addressable memory size, a byte). This would be
a terrible waste of memory bandwidth and register usage.

@@

Bitslicing is the cryptographer's jargon for such a representation
change. In the case of \Skinny{}, we observe that only \coqe!shiftrows_!
imposes a strict composition order of \coqe!Rows.T! followed by
\coqe!Cols.T!. Aside from that, we can commute \coqe!Slice8.T! out the
composition. We would thus have the type \coqe!Rows.T (Cols.T bool)!
representing 16 bits and fitting snugly in a 32 bits machine word. The
overall composition \coqe!Slice8.T (Rows.T (Cols.T bool))! would take
8 registers in total, imposing a very reasonable amount of register
pressure to the CPU.
%
In effect, to return back to the jargon of compiler designers, we
propose to turn a structure-of-arrays (SoA) into an
array-of-structures (AoS), only we are dealing with bit-level
quantities here.

>>>>

If we were to adopt \coqe!state! as our actual representation, the
memory usage of the resulting program would be quite poor. It would take
at least 128 bytes to store that many bits (assuming that booleans are
stored in the smallest addressable memory size, a byte). This would be
a terrible waste of memory bandwidth and register usage.

@@

Bitslicing is the cryptographer's jargon for such a representation
change. In the case of \Skinny{}, we observe that only \coqe!shiftrows_!
imposes a strict composition order of \coqe!Rows.T! followed by
\coqe!Cols.T!. Aside from that, we can commute \coqe!Slice8.T! out the
composition. We would thus have the type \coqe!Rows.T (Cols.T bool)!
representing 16 bits and fitting snugly in a 32 bits machine word. The
overall composition \coqe!Slice8.T (Rows.T (Cols.T bool))! would take
8 registers in total, imposing a very reasonable amount of register
pressure on the CPU.
%
In effect, to return back to the jargon of compiler designers, we
propose to turn a structure-of-arrays (SoA) into an
array-of-structures (AoS), only we are dealing with bit-level
quantities here.
